
---
title: "Business Intelligence Project"
author: "Sadiki Hamisi"
date: "10/09/2023"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

|                                              |     |
|----------------------------------------------|-----|
| **Student ID Number**                        | 135232 |
| **Student Name**                             | sadiki Hamisi |
| **BBIT 4.2 Group**                           | A |
| **BI Project Group Name/ID (if applicable)** |  |

# Setup Chunk

**Note:** the following KnitR options have been set as the global defaults: <BR> `knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(
  warning = FALSE,
  collapse = FALSE
)
```

# Understanding the Dataset (Exploratory Data Analysis (EDA))

## Loading the Dataset

### Source:

The dataset that was used can be downloaded here: *\<provide a link\>*

### Reference:

*\<Cite the dataset here using APA\>\
Refer to the APA 7th edition manual for rules on how to cite datasets: <https://apastyle.apa.org/style-grammar-guidelines/references/examples/data-set-references>*

```{r Dataset Loader}
library(readr)

# Provide the executable R code inside the various code chunks as guided by the lab work.
```

...to be continued

code for dataset loading.

1. The code begins by loading the `readr` library, which provides functions for reading CSV files and controlling the data types of columns.

2. It reads the CSV file "dataset.csv" located in the "data/transforms/" directory and stores the data in the "stock_ror_dataset" data frame. The `read_csv` function is used for this purpose.

3. Within the `col_types` argument, the code specifies the column data types for the columns in the CSV file. In this case, it focuses on the "Disease" column.

4. The "Disease" column is assigned the data type of a factor using the `col_factor` function. A factor is a data type in R used for categorical variables. It's similar to an enumerated type in other programming languages. Factors are used when you have a fixed set of categories or levels for a variable.

5. The `levels` argument within `col_factor` specifies the possible values or levels that the "Disease" column can take. These levels are provided as a character vector and include various medical conditions.

6. The levels list starts with "Disease" itself, followed by a list of specific medical conditions. The levels appear to be categorized as various diseases and health conditions.

7. Some of the comments in the code (e.g., "# nolint") are comments for code linters or style checkers and do not affect the code's functionality.

Overall, this code is designed to read a CSV file and specify the "Disease" column as a factor variable with predefined levels representing different medical conditions. The levels provide a categorical structure for the data in the "Disease" column, making it easier to work with categorical data in R.